Analyzing the Citation Rate of a Scientific Paper Using ML and Graph Algorithms

### 2024-12-19 paper/paper.tex
Added conlusion + small fixes

\subsection{Our solution}

\end{document}

>>>>

\subsection{Our solution}
In search of a better solution, we tried GCN and GCNwLinear models with different types of node embeddings: random embeddings (learnable), text/graph-only embeddings and their concatenation (we tried using each of them separately, as well as in combination with each other). In addition, we went through the following parameters:
\begin{verbatim}
n_layers = 6
random_emb_size = 32
hidden_dim = 128
crop_df = False
tune_embs = True
add_reverse_edges = True
dropout=0.2
lr = 5e-4
node_emb_size = 64
\end{verbatim}
Each parameter speaks for itself except of \textbf{crop\_df} which is responsible for getting rid of the imbalance of classes in the dataset by removing some samples or not. Above, is the best subset of these hyperparameters, we were able to find for GCNwLinear model, which uses combination of text and node embeddings. The metrics achieved by this model are shown below:
\begin{table}[h]
\centering
\begin{tabular}{c c  c c c}
\hline\hline
 & & \multicolumn{3}{c}{Metrics} \\
\cline{3-5}
Classification model & Embeddings & \multirow{2}{*}{Accuracy} & \multicolumn{2}{c}{F1 score} \\
 & & & Macro & Weighted \\
\hline
\multirow{1}{*}{GCNwLinear} & Concatenated text and node embs & 0.58 & 0.54 & 0.59 \\
\hline
\end{tabular}
\caption{Final metrics.}
\label{table:final_metrics}
\end{table}
\section{Conclusion}
\tab Unlike the other works, we implemented the combination of text embeddings and node embeddings to complete the task of predicting citation rate. As we can see, on the chosen dataset, this method performed better than other methods from previous works on this subject. Not only were the metrics improved, but also the balance of predicted citation rates became better, not ignoring or overemphasizing any particular class. This goes to show, that GNN models have a bright future regarding the task of predicting citation rates.
As per usual, those models should be tested more on different datasets and different areas of scientific publication, to confirm its effectiveness and achieve better results.
\end{document}
